Multi-line Intensity Mapping

### 2019-04-15 paper/ms.tex
Change to SNR instead of SNR^2
Update preamble
Move figures around
Add section on simple CO forecasts (at one z)

\newcommand{\GHz}{\ensuremath{\text{GHz}}}

@@

Inverting this matrix we find that the covariance matrix of the bias factors is,
\beq \label{eq:covmat_tf_wn}
C = F^{-1} = \frac{1}{4V_k^2}
\begin{pmatrix}
\frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_2^2B_3^2} & \frac{-B_1^2N_2N_3 - B_2^2N_3N_1 + B_3^2N_1N_2}{B_1B_2B_3^2} & \frac{-B_1^2N_2N_3 + B_2^2N_3N_1 - B_3^2N_1N_2}{B_1B_2^2B_3} \\
\frac{-B_1^2N_2N_3 - B_2^2N_3N_1 + B_3^2N_1N_2}{B_1B_2B_3^2} & \frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_3^2B_1^2} & \frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} \\
\frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} & \frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} & \frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_1^2B_2^2}
\end{pmatrix}
\text{.}
\eeq
Examining the diagonal components we have that:
\beq \label{eq:var_bias_tf_wn}
\begin{split}
C_{1,1} = \sigma_{B_1}^2 &= \frac{1}{4V_k^2} \left( B_1^2 \frac{N_2N_3}{B_2^2B_3^2} + N_1(\frac{N_2}{B_2^2} + \frac{N_3}{B_3^2}) \right) \\
\implies \frac{\sigma_{B_1}^2}{B_1^2} &= \frac{1}{4V_k^2} \left( \frac{N_1N_2}{B_1^2B_2^2} + \frac{N_2N_3}{B_2^2B_3^2} + \frac{N_3N_1}{B_3^2B_1^2} \right)\text{.}
\end{split}
\eeq
The symmetry of this result implies that,
\beq \label{eq:frac_error_same}
\frac{\sigma_{B_1}^2}{B_1^2} = \frac{\sigma_{B_2}^2}{B_2^2} = 
\frac{\sigma_{B_3}^2}{B_3^2}\text{.}
\eeq
Unfortunately the surprising result that the fractional error on each line is
the same only holds in the three field case.

@@

\subsection{\CO{} Forecasts for CCAT-p and CONCERTO} \label{ssec:forecasts_tf}
Armed with some intuition from the simple white noise-dominated case, we now
turn to forecasting constraints that can be placed on the CO bias factors. Our
modelling of the \CO{} intensity as a function of redshift follows
\citet{2016ApJ...825..143L} and is outlined in Appendix~\ref{app:co_int}. We
assume that $b_i=3$ for each \CO{} line.

>>>>

\newcommand{\MHz}{\ensuremath{\text{MHz}}}
\newcommand{\GHz}{\ensuremath{\text{GHz}}}

@@

Inverting this matrix we find that the covariance matrix of the bias factors is,
\beq \label{eq:covmat_tf_wn}
C = F^{-1} = \frac{1}{4V_k^2}
\begin{pmatrix}
\frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_2^2B_3^2} & \frac{-B_1^2N_2N_3 - B_2^2N_3N_1 + B_3^2N_1N_2}{B_1B_2B_3^2} & \frac{-B_1^2N_2N_3 + B_2^2N_3N_1 - B_3^2N_1N_2}{B_1B_2^2B_3} \\
\frac{-B_1^2N_2N_3 - B_2^2N_3N_1 + B_3^2N_1N_2}{B_1B_2B_3^2} & \frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_3^2B_1^2} & \frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} \\
\frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} & \frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} & \frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_1^2B_2^2}
\end{pmatrix}
\text{.}
\eeq
Examining the diagonal components we have that:
\beq \label{eq:var_bias_tf_wn}
\begin{split}
C_{1,1} = \sigma_{B_1}^2 &= \frac{1}{4V_k^2} \left( B_1^2 \frac{N_2N_3}{B_2^2B_3^2} + N_1(\frac{N_2}{B_2^2} + \frac{N_3}{B_3^2}) \right) \\
\implies \frac{\sigma_{B_1}^2}{B_1^2} &= \frac{1}{4V_k^2} \left( \frac{N_1N_2}{B_1^2B_2^2} + \frac{N_2N_3}{B_2^2B_3^2} + \frac{N_3N_1}{B_3^2B_1^2} \right)\text{.}
\end{split}
\eeq
The symmetry of this result implies that,
\beq \label{eq:frac_error_same}
\frac{\sigma_{B_1}}{B_1} = \frac{\sigma_{B_2}}{B_2} = 
\frac{\sigma_{B_3}}{B_3}\text{.}
\eeq
Unfortunately the surprising result that the fractional error on each line is
the same only holds in the three field case.

@@

\subsection{Three-field \CO{} Forecasts for CCAT-p} \label{ssec:forecasts_tf}
\begin{figure}[h!]
\begin{center}
\includegraphics{fig/CO_tf.pdf}
\end{center}
\caption{Constraints that can be placed on the fluctuations of the \CO(6-5),
\CO(5-4), and \CO(4-3) lines with CCAT-p at $z_{\text{obs}} = 0.88$. This
Figure is purely illustrative, as we do not include noise contributions from
residual foreground contamination or interloper/extraloper lines. According to
our simple \CO{} model, we have that $B_{\text{6-5}}, B_{\text{5-4}},
B_{\text{4-3}} = 151, 183, 232\,\text{Jy}/\text{str}$. Using the instrumental
specifications in \citet{2018arXiv181208135C}, we find that $N_{\text{6-5}},
N_{\text{5-4}}, N_{\text{4-3}} = 5.1\times10^9, 1.4\times10^9,
5.4\times10^8\,\left(\text{Jy}/\text{str}\right)^2\,\Mpc^3$. We find the same
behavior as in Figure~\ref{fig:tf_Nconst}, where the best-measured line is
strongly negatively degenerate with the second-best measured line, the
best-measured and worst-measured are slightly negatively degenerate, and the
second-best measured line and the worst-measured are slightly positively
degenerate. }
\label{fig:CO_tf}
\end{figure}

Armed with some intuition from the simple white noise-dominated case, we now
turn to forecasting constraints that can be placed on the \CO{} bias factors.
Our modelling of the \CO{} intensity as a function of redshift follows
\citet{2016ApJ...825..143L} and is outlined in Appendix~\ref{app:co_int}. We
assume that $b_i=3$ for each \CO{} line.

At $z=0.88$, the lines \CO(6-5) ($\nu_{\text{obs}} = 367\,\MHz$), \CO(5-4)
($\nu_{\text{obs}} = 306\,\MHz$), and \CO(4-3) ($\nu_{\text{obs}} =
245\,\MHz$) are all in the observing band of CCAT-p. We only include
instrumental noise for this Subsection, neglecting foreground and
interloper/extraloper contamination. We simply want to place the result of
Section~\ref{ssec:tf_noisedom} in the context of an actual experiment.

Using our \CO{} modelling, we find that $B_{\text{6-5}}, B_{\text{5-4}},
B_{\text{4-3}} = 151, 183, 232\,\text{Jy}/\text{str}$ at $z=0.88$. Using the
instrumental specifications in \citet{2018arXiv181208135C}, we find that
$N_{\text{6-5}}, N_{\text{5-4}}, N_{\text{4-3}} = 5.1\times10^9,
1.4\times10^9, 5.4\times10^8\,\left(\text{Jy}/\text{str}\right)^2\,\Mpc^3$. We
assume the instrumental noise is white, but note that in this case the
noise-dominated assumption is mildly broken. The worst case is that of the
\CO(4-3) line, where on a scale of $k\sim0.01\,\Mpc^{-1}$ we have that
$P_{\text{4-3}} \sim 3N_{\text{4-3}}$. Again, this Subsection is purely
illustrative, and we will rectify these assumptions in the next Section.

We assume a bandwidth of $60\,\MHz$ for the line \CO(6-5). This corresponds to
a redshift band of width $\Delta z = 0.16$. We resize the \CO(5-4) and
\CO(4-3) bands to have the same extent in redshift space, which means slightly
scaling the frequency bandwidth --- in this case, the bandwidths are $50$ and
$40\,\MHz$, respectively. In Figure~\ref{fig:CO_tf} we show the constraints
that can be placed on each of $B_{\text{6-5}}$, $B_{\text{5-4}}$, and
$B_{\text{4-3}}$. The line \CO(4-3) is measured to the best intrinsic \SN{},
followed by \CO(5-4) and then \CO(6-5). We find the same behavior as in
Section~\ref{ssec:tf_noisedom}, where the best-measured line is strongly
negatively degenerate with the second-best measured line, the best-measured
and worst-measured are slightly negatively degenerate, and the second-best
measured line and the worst-measured are slightly positively degenerate.
However, we find that CCAT-p should be able to make a measurement of each bias
factor using the three-field approach.
